---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prcPhenoAge

<!-- badges: start -->
<!-- badges: end -->

The goal of prcPhenoAge is to perform a calculation of PhenoAge (2018) while subscoring the epigenetic age into the portion of PhenoAge reliant upon beta values annotated to be in PRC associated CpGs, and non-PRC associated CpGs. The PRC annotation is from the 27K CpGs, but the information is applicable to arrays of 450K and Illumina EPIC data.

## Installation

You can install the released version of prcPhenoAge from [GitHub](https://github.com/MorganLevineLab/prcPhenoAge) with:

``` r
devtools::install_github("MorganLevineLab/prcPhenoAge")
```

## Example

Here is a template code using example data (Lehne et al. 2015) available as part of this package:

```{r example}
library(prcPhenoAge)
data("exampleBetas")
data("examplePheno")
PRC_PhenoAge <- calcnonPRCPhenoAge(exampleBetas, examplePheno, imputation = F)
PRC_PhenoAge <- calcPRCPhenoAge(exampleBetas, PRC_PhenoAge, imputation = F)
PRC_PhenoAge
```

